---
title: "eds221-day4morning"
format: html
editor: visual
---

Practice writing functions!

```{r}
double_value <- function(my_dollars){
  print(2 * my_dollars)
}
double_value(4)
```

```{r}
monthly_income <- c(42.5, 61, 34) 
double_value(monthly_income)
```

Create a function that returns an awesome restaurant name given a cool animal and your favorite food

```{r}
name_restaurant <- function(animal, food){
  print(paste0(animal,food))
}

name_restaurant("hawk", "pizza")
```

Given temperature in degrees fahreinheit, write a function that converts it to Celcius

```{r}
f_to_c <- function(temp_f){
temp_C = (temp_f-32)*(5/9)
print(temp_C)
}
f_to_c(temp_f = 100)

```

Create a function that given inputs of age and hometown, returns "I am \_\_ years old, and I'm from \_\_\_\_"

```{r}
exclamation <- function(age, hometown){
  says = paste0("I am ", age, " years old, and I'm from ", hometown)
  print(says)
}
exclamation(32, "Cornucopia")
```

# Functions with conditionals 

```{r}
calculate_animal_age <- function(species, age_human_years) {
  if (species == "dog") {
    age_human_years * 7 
  } else if (species == "goat") {
    age_human_years * 4.7 
  } else{
    print("Please enter dog or goat.")
  }
}
```

```{r}
calculate_animal_age(species = "dog", age_human_years = 10)
calculate_animal_age(species = "goat", age_human_years = 4 )
calculate_animal_age(species = "whale", age_human_years = 10)
```

Write a function that, given temperature in kelvin, if a user selects "metric" to the scale then return degrees Celcius, or if they select "Imperial" then return degrees in Fahrenheit.

```{r}
kelv_convert<- function(scale, kelvin){
  if(scale == "metric"){
    k_to_c =  kelvin - 273.15
    print(k_to_c)
  } else if (scale == "imperial"){
    k_to_f = ((kelvin - 273.15)*1.8) + 32
    print(k_to_f)
  } 
}
kelv_convert("metric", 44)

```
change
